\textsc{Atomic modeling of argon}\\ \footnotesize{\textsc{Project 5 --- FYS3150}}

### 2015-12-09 projects/project_5/molecular_dynamics/article/article.tex
did references properly

\begin{thebibliography}{9}
\bibitem{folding}
    Levitt, M., \& Warshel, A., `Computer simulation of protein folding`, Nature, Vol. 253, No. 5494. Available from: \url{http://csb.stanford.edu/levitt/Levitt_NAT75_folding.pdf}
\bibitem{thermoprotein}
    Cooper, A. `Thermodynamic fluctuations in protein molecules`, Proceedings of the National Academy of Sciences of the United States of America, Vol. 73, No. 8. Available from: \url{http://www.pnas.org/content/73/8/2740.full.pdf}
\bibitem{liquid_argon}
    Rahman, A., `Correlations in the Motion of Atoms in Liquid Argon`, Physical Review, Volume 136, No. 2A. Available from: \url{http://journals.aps.org/pr/pdf/10.1103/PhysRev.136.A405}.
\bibitem{min_image}
    `Periodic boundary conditions` (wiki article), December 7, 2015. Available from: \url{https://en.wikipedia.org/wiki/Periodic_boundary_conditions#Practical_implementation:_continuity_and_the_minimum_image_convention} [November 13, 2015]
\bibitem{equipar} 
    `Equipartition theorem` (wiki article), December 7, 2015.
    Available from: \url{https://en.wikipedia.org/wiki/Equipartition\_theorem} [November 21, 2015]
\bibitem{virial} 
    `Virial theorem` (wiki article), December 7, 2015, \url{https://en.wikipedia.org/wiki/Virial_theorem} [October 7, 2015]
\end{thebibliography}
\end{document}

>>>>

\begin{thebibliography}{9}
\bibitem{thermoprotein}
    Cooper, A. (1976). Thermodynamic fluctuations in protein molecules. Proceedings of the National Academy of Sciences, 73, 2740-2741. Retrieved December 9, 2015, from \url{http://www.pnas.org/content/73/8/2740.full.pdf}
\bibitem{equipar} 
    Equipartition Theorem. (2015, November 21). Retrieved December 7, 2015, from \url{https://en.wikipedia.org/wiki/Equipartition_theorem}
\bibitem{folding}
    Levitt, M., \& Warshel, A. (1975). Computer simulation of protein folding. Nature, 253, 694-698. Retrieved December 7, 2015, from \url{http://csb.stanford.edu/levitt/Levitt_NAT75_folding.pdf}
\bibitem{min_image}
    Periodic boundary conditions. (2015, November 13). Retrieved December 7, 2015, from \url{https://en.wikipedia.org/wiki/Periodic_boundary_conditions}
\bibitem{liquid_argon}
    Rahman, A. (1964). Correlations in the Motion of Atoms in Liquid Argon. Phys. Rev. Physical Review, 126(2A). Retrieved December 7, 2015, from \url{http://journals.aps.org/pr/pdf/10.1103/PhysRev.136.A405}
\bibitem{virial} 
    Virial Theorem. (2015, October 7). Retrieved December 7, 2015, from \url{https://en.wikipedia.org/wiki/Virial_theorem}
\end{thebibliography}
\end{document}
